Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-22 paper/aldebaran.tex
fix typo, affiliation, acknowlegement

\author{Tim White}
\affiliation{Stellar Astrophysics Centre, Department of Physics 
and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

@@

Our new approach to asteroseismic data analysis, based on Continuous Auto-Regressive Moving Average (CARMA) models, can extract exoplanet signals together with measures of \numax from sparse and irregularly-sampled time series. An all-sky survey planetary companions to precisely measure the masses of all nearby red giant stars is feasible with this new approach, and the required data either already exist in large exoplanet surveys, or are easy to obtain with ground-based telescopes.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.

This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and NASA's Astrophysics Data System. The \kepler data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  This work made use of the \textsc{IPython} package \citep{PER-GRA:2007}; SciPy \citep{scipy};  \textsc{matplotlib}, a \textsc{Python} library for publication quality graphics \citep{Hunter:2007}; \textsc{Astropy}, a community-developed core \textsc{Python} package for astronomy \citep{2013A&A...558A..33A}; and \textsc{NumPy} \citep{van2011numpy}. Some of the acknowledgements were compiled using the Astronomy Acknowledgement Generator.

>>>>

\author[0000-0002-6980-3392]{Timothy R. White}
\affiliation{Stellar Astrophysics Centre, Department of Physics 
and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

@@

Our new approach to asteroseismic data analysis, based on Continuous Auto-Regressive Moving Average (CARMA) models, can extract exoplanet signals together with measures of \numax from sparse and irregularly-sampled time series. An all-sky survey to find planetary companions and to precisely measure the masses of all nearby red giant stars is feasible with this new approach, and the required data either already exist in large exoplanet surveys, or are easy to obtain with ground-based telescopes.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation. TRW acknowledges the support of the Villum Foundation (research grant 10118).
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and NASA's Astrophysics Data System. The \kepler data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  This work made use of the \textsc{IPython} package \citep{PER-GRA:2007}; SciPy \citep{scipy};  \textsc{matplotlib}, a \textsc{Python} library for publication quality graphics \citep{Hunter:2007}; \textsc{Astropy}, a community-developed core \textsc{Python} package for astronomy \citep{2013A&A...558A..33A}; and \textsc{NumPy} \citep{van2011numpy}. Some of the acknowledgements were compiled using the Astronomy Acknowledgement Generator.
